%%
%% Author: Moritz
%% 11.03.2018
%%

% Preamble
\documentclass[../Pflichtenheft.tex]{subfiles}
\begin{document}
    \begin{longtable}{p{4cm} p{4cm} p{6cm}}
        \textbf{Akonto} & {Deposit} & A deposit is money that a guest pays before using services of the hotel. \\[0.5cm]
        \textbf{Aufenthalt} & {Stay} & A period of staying temporarily as a guest. \\[0.5cm]
		\textbf{Auslastung} & {Occupancy rate} & Is a rate which shows the percentage of booked rooms compared to total rooms. \\[0.5cm]
        \textbf{Back-Office} & {Back-Office} & All the operations that are not directly related to the physical guest are carried out in the back office. These are broadly the activities to be carried out prior to arrival and after departure of the guest. \\[0.5cm]
		\textbf{Belegungsplan} & {Booking plan} & Is a plan which gives an overview of all bookings. \\[0.5cm]
        \textbf{Berechtigungen} & {Permissions} & Methods to assign access rights to specific users and/or groups of users. \\[0.5cm]
        \textbf{Check-In} & {Check-In} & The process of allocate a guest to the corresponding room(s). \\[0.5cm]
        \textbf{Check-Out} & {Check-Out} & The process when guests terminate their stay at the hotel. \\[0.5cm]
        \textbf{Doppelbelegung} & {Double occupancy} & When a room has two reservation assigned to it, for a specific timespan. Also when a category has more reservations then rooms in this timespan. \\[0.5cm]
        \textbf{Extraleistung} & {Extra service} & A product or service which is not included in the room price, such as products from the minibar or services from a laundry. \\[0.5cm]
        \textbf{Front-Office} & {Front-Office} & The front office - area includes all processes that are performed directly at the reception in contact with the guests. \\[0.5cm]
        \textbf{Gast} & {Guest} & A person, group or company which is lodging at a hotel and uses the services. \\[0.5cm]
        \textbf{Gast des Hauses} & {Guest of the house} & A guest which has free lodging at the hotel. \\[0.5cm]
        \textbf{Geburtsdatum} & {Date of birth} & On which date the person was born. \\[0.5cm]
        \textbf{Geschlecht} & {Sex} & To which gender group a human can be categorized. \\[0.5cm]
		\textbf{Hotelleistung} & {Hotel service} & Is a service which is offered by the hotel. \\[0.5cm]
        \textbf{Individualgast} & {Individual guest} & A person lodging at a hotel and uses the services. \\[0.5cm]
		\textbf{Jahresabschluss} & {Annual closure} & Is a print out of the annual reports, containing the core data. \\[0.5cm]
		\textbf{Journal} & {Journal} & A record of the daily proceedings in the hotel. \\[0.5cm]
        \textbf{Kategorie} & {Category} & The rooms are divided into different classes. \\[0.5cm]
        \textbf{Kontingent} & {Quota} & A quota is a pre-order of rooms, which can be assign by the travel agency on their own. \\[0.5cm]
        \textbf{Kreditgrenze} & {Credit limit} & Credit limit which is granted to a individual guest. This limit can be changed at the Check-In. \\[0.5cm]
		\textbf{Listenpreis} & {List price} & Is the price which is set for a roomcategory. \\[0.5cm]
		\textbf{Mindestpreis} & {Minimum price} & Is a price which cannot be undercut. \\[0.5cm]
        \textbf{Monatsabschluss} & {Monthly closure} & Is a print out of the monthly reports, containing the core data. \\[0.5cm]
        \textbf{Option} & {Option} & An option is a specific condition which is linked to a reservation and must be fulfilled to confirm the reservation. \\[0.5cm]
        \textbf{Optionsdatum} & {Option date} & Date by which the option must be fulfilled. \\[0.5cm]
        \textbf{Out of Order} & {Out of order} & Status of a room. The room with this status can not be occupied. \\[0.5cm]
        \textbf{Package} & {Package} & The individual guest or the booking agency can choose from a variety of offers which can contain different services. \\[0.5cm]
        \textbf{Prognose} & {Forecast} & Room occupancy and reservation preview. In the forecast the room reservations are shown. \\[0.5cm]
        \textbf{Rechnung} & {Invoice} & A list of goods consumed or services used, with a statement of the sum due for these. \\[0.5cm]
        \textbf{Rechnung erstellen} & {Create invoice} & During this process all services a guest has used, are listed. All the prices are summed up and taxes are added. \\[0.5cm]
        \textbf{Rechnung legen} & {To render account} & Prints the invoice and confirms the payment. \\[0.5cm]
        \textbf{Rechnung teilen} & {Partition of a bill} & Splitting a bill offers the possibility that people can share their bill. \\[0.5cm]
        \textbf{Rechnungsbestätigung} & {Confirmation of reserveration} & Is a binding confirmation that the reservation is definite. \\[0.5cm]
        \textbf{Rechnungsposition} & {Invoice line item} & A consumed good or service. \\[0.5cm]
        \textbf{Reservierung} & {Reservation} & An arrangement whereby a room of a category is kept for someone. \\[0.5cm]
        \textbf{Stammdaten} & {Core data} & Key data required for operating a hotel. Such as hotel name, number of rooms, etc. \\[0.5cm]
        \textbf{Stornofrist} & {Cancellation deadline} & The cancellation deadline determine the amount of the cancellation fee, depending on the cancellation period. \\[0.5cm]
		\textbf{Stornogebühr} & {Cancellation fee} & Is a charge produced as a consequence for canceling the booking contract. \\[0.5cm]
		\textbf{Überbuchung} & {Overbooking} & Is a booking which exceeds the category room capacity. \\[0.5cm]
        \textbf{Überbuchungsgrenze} & {Overbooking border} & Limit how many reservations are accepted over the number of rooms. \\[0.5cm]
        \textbf{Vertragspartner} & {Contracting party} & A written agreement over the category prices and/or room quota. \\[0.5cm]
        \textbf{Walk-In} & {Walk-In} & A customer or guest without an reservation. \\[0.5cm]
        \textbf{Zahlungsart} & {Payment types} & The different possible methods to payment (credit card, cash, ect.) with abbrevation. \\[0.5cm]
		\textbf{Zimmer} & {Room} & A bedroom which can be occupied. \\[0.5cm]
		\textbf{Zimmernummer} & {Room number} & Is a numeration which cleary identifies a room. \\[0.5cm]
        \textbf{Zimmerstatus} & {Room status} & Is a description for the room which can be \begin{itemize}
                                                                                               \item OCCUPIED - CLEANED
                                                                                               \item OCCUPIED - UNCLEANED
                                                                                               \item FREE - CLEANED
                                                                                               \item FREE - UNCLEANED
                                                                                               \item OUT OF ORDER
        \end{itemize} \\[0.5cm]
		\textbf{Zimmerzuteilung} & {Room assignment} & Assigning the rooms with a guest on a given day. \\[0.5cm]
        \textbf{Zusatzleistung} & {Additional service} & Services that can be booked before your stay, such as half-board or a garage, etc. \\[0.5cm]
        \textbf{Zwischenrechnung} & {Pro forma invoice} & A list of all consumptions incirred up to this time and payments on a account for a guest. \\[0.5cm]
	\end{longtable}
\end{document}